---
title: "Probability"
subtitle: "Week 06, Day 1; Homework"
author: "Miles Drake"
date: 2020-03-30
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_float: true
---

```{r knitr, include = FALSE}
knitr::opts_chunk$set(error = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(gtools)
library(prob)
library(tidyverse)
```

# Question 1
> If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
d6_lt5 <- rolldie(1) %>% 
  filter(X1 < 5)
nrow(d6_lt5)/nrow(
  rolldie(1)
)
```

# Question 2
> How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
nrow(
  rolldie(3)
)
```

# Question 3
> In an experiment where we roll four dice:

## Question 3a
> How many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals \(5\), \(6\) or \(7\))?

```{r}
total_equals_5_6_7 <- rolldie(4) %>% 
  mutate(
    "sum" = X1 + X2 + X3 + X4
  ) %>% 
  filter(
    sum %in% c(5, 6, 7)
  )
nrow(total_equals_5_6_7)
```

## Question 3b
> What is the probability of this event?

```{r}
nrow(total_equals_5_6_7)/nrow(rolldie(4))
```

## Question 3c
> What assumptions do we apply in answering part iii?

We assume that the observations are independent. We also assume that the dice are fair.

# Question 4
>  Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
1/nrow(
  permutations(
    n = 5,
    r = 5
  )
)
```

# Question 5
> I roll six dice:

## Question 5a
> What is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?

```{r}
1/nrow(
  rolldie(6)
)
```

## Question 5b
> What is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

```{r}
nrow(
  permutations(
    n = 6,
    r = 6
  )
) / 
  nrow(
    rolldie(6)
  )
```

# Question 6
> If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

```{r}

```
