---
title: "Conditionals, Functions, and Loops"
subtitle: "Week 01, Day 5; Homework"
author: "Miles Drake"
date: 2020-02-28
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: true
---

```{r knitr, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r libraries, include = FALSE}
library(dplyr)
```

# MVP

## `if` Statements and Functions

### Algebra

```{r}
m15a4 <- function(input) {
  output <- input * 15
  output <- output + 4
  return(output)
}
```

```{r}
m15a4(1:10)
```

#### Thought Exercise: Verbose Output

The following just tests an idea I had about making a function give a "verbose" output. If a user wants to see what function `m15a4` is doing to the input to reach the output, they can use `m15a4_verbose(x, verbose = TRUE)` to get a character output similar to an algebraic expression.

This is, ultimately, unnecessary because it would be best to include this information in help files. It was good practice, though.

```{r}
m15a4_verbose <- function(input, verbose = FALSE) {
  for (number in input) {
    output <- input * 15
    output <- output + 4
    if (verbose == TRUE) {
      output <- paste("15 *",input,"+ 4 =",output)
    }
    return(output)
  }
}
```

```{r}
m15a4_verbose(1, verbose = TRUE)
```

### Birds

```{r}
isBird <- function(input) {
  birdVector <- c("goose", "duck", "pigeon")
  bird <- casefold(input, upper = FALSE)
  paste(
    input,
    ifelse (bird %in% birdVector,"is","is NOT"),
    "a bird."
    )
}
```

```{r}
isBird(list("Duck", "Goose", ":cool-doge:"))
```

### Numbers

```{r}
m10 <- function(input) {
  for (number in input) {
    if (is.numeric(number) == TRUE) {
      output <- number * 10
      output <- paste(number,"* 10 =",output)
      return(output)
    } else {
      paste(input,"is not a number.")
    }
  }
}
```

```{r}
m10(1)
```

## `ifelse()`, `recode()`, and `case_when()`

### Big or Small

```{r}
big <- list()

# ifelse()
big$ifelse <- function (input) {
  ifelse(
  input > 10,
  print("Big"),
  print("Small")
  )
}

# recode()
big$recode <- function (input) {
  difference <- input - 10
  difference <- difference/abs(difference)
  difference <- gsub(NaN, -1, difference)
  recode(
    difference,
    `1` = "Big",
    `-1` = "Small"
  )
}

# case_when()
big$casewhen <- function (input) {
  case_when(
    input > 10 ~ "Big",
    input <= 10 ~ "Small"
  )
}
```

```{r}
sizes <- c(13, 15, 10, 8, 22)
```

```{r include=FALSE}
bigSizes <- list(
  ifelse = big$ifelse(sizes),
  recode = big$recode(sizes),
  casewhen = big$casewhen(sizes)
)
```

```{r}
bigSizes$ifelse
bigSizes$recode
bigSizes$casewhen
```

`case_when()` provides the simplest solution.

My solution for `recode()` works, and it does take all realistic values, but understanding it requires some maths knowledge.

### Fruity Animals

```{r}
animals <- list()

# ifelse()
animals$ifelse <- function (input) {
  ifelse (
    input == "apple",
    print("alpaca"),
    ifelse (
      input == "banana",
      print("bonobo"),
      ifelse (
        input == "cherry",
        print("chipmunk"),
        NA
      )
    )
  )
}

# recode()
animals$recode <- function (input) {
  recode(
    input,
    "apple" = "alpaca",
    "banana" = "bonobo",
    "cherry" = "chipmunk"
  )
}

# case_when()
animals$casewhen <- function (input) {
  case_when(
    input == "apple" ~ "alpaca",
    input == "banana" ~ "bonono",
    input == "cherry" ~ "chipmunk"
  )
}
```

```{r}
fruit <- c("apple", "apple", "banana", "cherry", "cherry")
```

```{r include=FALSE}
fruityAnimals <- list(
  ifelse = animals$ifelse(fruit),
  recode = animals$recode(fruit),
  casewhen = animals$casewhen(fruit)
)
```

```{r}
fruityAnimals$ifelse
fruityAnimals$recode
fruityAnimals$casewhen
```

`recode()` and `case_whee()` are both simple blocks of code, with similar lengths. Of the two, `recode()` is more legible.

### `power(couples)`

```{r}
ageDifference <- list()

# ifelse()
ageDifference$ifelse <- function (husband, wife) {
  ifelse(
    husband == wife,
    print("Same age"),
    ifelse(
      husband > wife,
      print("Husband older"),
      print("Wife older")
    )
  )
}

# recode()
ageDifference$recode <- function (husband, wife) {
  difference <- husband - wife
  difference <- difference/abs(difference)
  difference <- gsub(NaN, 0, difference)
  recoded <- recode(
    difference,
    `0` = "Same age",
    `1` = "Husband older",
    `-1` = "Wife older"
  )
}

# case_when()
ageDifference$casewhen <- function (husband, wife) {
  case_when(
    husband == wife ~ "Same age",
    husband > wife ~ "Husband older",
    husband < wife ~ "Wife older"
  )
}
```

```{r}
age <- list(
  husband = c(28L, 35L, 32L, 31L, 29L),
  wife = c(29L, 30L, 36L, 31L, 22L)
)
```

```{r include=FALSE}
ageComparison <- list(
  ifelse = ageDifference$ifelse(age$husband, age$wife),
  recode = ageDifference$recode(age$husband, age$wife),
  casewhen = ageDifference$casewhen(age$husband, age$wife)
)
```

```{r}
ageComparison$ifelse
ageComparison$recode
ageComparison$casewhen
```

`case_when()` provides the simplest block of code.

## Loops

```{r}
my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)
```

### `for`

```{r}
forLoop <- function (input){
  for (element in input) {
    if (is.character(element) == TRUE) {
      print(element)
    }
  }
}
```

```{r}
forLoop(my_list)
```

### `while`

```{r}
whileLoop <- function (input){
  currentValue <- 1
  stopValue <- length(input) + 1
  while (currentValue < stopValue) {
    if (is.character(input[[currentValue]]) == TRUE) {
      print(input[[currentValue]])
    }
    currentValue <- currentValue + 1
  }
}
```

```{r}
whileLoop(my_list)
```

### Putting It All Together

```{r}
cWhileLoop <- function (input){
  currentValue <- 1
  stopValue <- length(input) + 1
  output <- NULL
  while (currentValue < stopValue) {
    if (is.character(input[[currentValue]]) == TRUE) {
      output <- c(output, input[[currentValue]])
    }
    currentValue <- currentValue + 1
  }
  print(output)
}
```

```{r}
cWhileLoop(my_list)
```

# Extensions: Puzzles

## Multiplication Table

```{r}
matrixLoop <- function (){
  matrixTable <- matrix(0, nrow = 12, ncol = 12)
  rowCurrentValue <- 1
  rowStopValue <- 12
  colCurrentValue <- 1
  colStopValue <- 12
  while (colCurrentValue < colStopValue + 1) {
    while (rowCurrentValue < rowStopValue +1) {
      matrixTable[colCurrentValue, rowCurrentValue] <- colCurrentValue * rowCurrentValue
      rowCurrentValue <- rowCurrentValue +1
    }
    colCurrentValue <- colCurrentValue + 1
    rowCurrentValue <- 1
  }
  return(matrixTable)
}
```

```{r}
matrixLoop()
```

## Art Histogram

```{r}
art <- function (vector) {
  vector <- as.vector(vector, mode = "integer")
  finalOutput <- NULL
  for (number in vector) {
    output <- NULL
    repetitions <- number
    repeat {
      output <- c(output, "*")
      repetitions <- repetitions - 1
      if (repetitions == 0) {
        break
      }
    }
    finalOutput <- c(finalOutput, output, "\n")
  }
  cat(finalOutput)
}
```

```{r}
art(c(3, 1, 7, 4, 2))
```
