---
title: "Dates and Times"
date: "2020-04-07"
---

```{r include = FALSE}
library(feasts)
library(lubridate)
library(nycflights13)
library(tidyverse)
library(tsibble)
library(tsibbledata)
```

```{r include = FALSE}
library(nycflights13)
```

This homework covers dates, times, and the `lubridate` package. We will be working with datasets from the `nycflights13` package, and these starting variables:

```{r}
date1 <- ymd_hms("2017-04-22 22:01:18")
date2 <- ymd_hms("2001-11-07 10:09:56")
```

```{r}
date1
date2
```

The `nycflights13` package contains five different datasets:

- `airlines`: airline names,
- `airports`: metadata about airports,
- `flights`: on time flight data for all flights that departed NYC,
- `planes`: plane metadata for plane tailnumbers, and
- `weather`: hourly meterological data.

## Question 1
*Extract the different components (year, month, mday, yday, wday) from the variable `date1.` Add the labels to the month and do not abbreviate the month labels.*

```{r}
year(date1)
month(date1, label = TRUE, abbr = FALSE)
mday(date1)
yday(date1)
wday(date1)
```

## Question 2
*Add 14 days to your `date1` variable and store it in a variable called `next_fortnight`.*

```{r}
next_fortnight <- date1 + ddays(14)
```

*Take away 10 years from your `date2` variable, and store it in `previous_decade`.*

```{r}
previous_decade <- date2 - dyears(10)
```

## Question 3
*Create a variable called `this_year` which contains today’s date. Then create an interval object which uses `this_year` and the `previous_decade` variable you made above. Store it in `interval_years`.*

```{r}
# Using lubridate's today() function instead of R's Sys.Date()
this_year <- today()
```

```{r}
lubridate::interval(
  ymd(
    paste(
      year(previous_decade),
      month(previous_decade),
      day(previous_decade),
      sep = "-"
    )
  ),
  ymd(this_year)
)
```

## Question 4
*Change the time zone of both your date variables to "America/New_York", and call them `nyc_date1` and `nyc_date2`.*

```{r}
nyc_date1 <- with_tz(date1, "America/New_York")
nyc_date2 <- with_tz(date2, "America/New_York")
```

```{r}
nyc_date1
nyc_date2
```

## Question 5
*Use the flights data from the `nycflights13` dataset. Make a date-time column called `departure_date` from the `year`, `month`, `day`, `hour`, and `minute` variables in the `flights` tibble.*

```{r}
flights <- flights %>% 
  mutate(
    departure_date = make_datetime(
      year,
      month,
      day,
      hour,
      minute
    )
  )
```

```{r}
head(flights)
```
