---
title: "Decathlon Analysis"
subtitle: "Week 04; Homework"
author: "Miles Drake"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_float: true
---

```{r knitr, include = FALSE}
knitr::opts_chunk$set(error = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries, include = FALSE}
library(tidyverse)
library(here)
```

```{r include = FALSE}
decathlon_data <- read_csv(
  here("clean_data/decathlon_clean.csv")
)

# Create a list to contain the analysis questions
decathlon_analysis <- list()
```

# Who had the longest long jump seen in the data?

```{r}
decathlon_analysis$long_jump_max <- decathlon_data %>% 
  filter(
    event_name == "Long Jump"
  ) %>% 
  select(
    name,
    event_score
  ) %>% 
  arrange(
    desc(event_score)
  ) %>% 
  head(1)
```

```{r echo = FALSE}
decathlon_analysis$long_jump_max
```

The longest recorded long jump in this data set was achieved by **`r decathlon_analysis$long_jump_max$name`**, with a distance of **`r decathlon_analysis$long_jump_max$event_score`** m.

# What was the average 100m time in each competition?

```{r}
decathlon_analysis$average_100m <- decathlon_data %>% 
  filter(
    event_name == "Sprint, 100m"
  ) %>% 
  group_by(
    competition
  ) %>% 
  summarise(
    mean_100m_time = mean(event_score)
  ) %>% 
  mutate(
    mean_100m_time = round(mean_100m_time, 2)
  )
```

```{r echo = FALSE}
decathlon_analysis$average_100m
```

The average 100 m sprint time in the **`r decathlon_analysis$average_100m$competition[1]`** was **`r decathlon_analysis$average_100m$mean_100m_time[1]`** s.
The average 100 m sprint time in the **`r decathlon_analysis$average_100m$competition[2]`** was **`r decathlon_analysis$average_100m$mean_100m_time[2]`** s.

# Who had the highest total points across both competitions?

```{r}
decathlon_analysis$points <- decathlon_data %>% 
  select(
    name,
    competition,
    points
  ) %>% 
  distinct() %>% 
  group_by(
    name
  ) %>% 
  summarise(
    total_points = sum(points)
  ) %>% 
  arrange(
    desc(total_points)
  ) %>% 
  head(1)
```

```{r echo = FALSE}
decathlon_analysis$points
```

The highest total points across both competitions was attained by
**`r decathlon_analysis$points$name`**,
with a total points score of
**`r format(decathlon_analysis$points$total_points, big.mark = ",", big.interval = 3L)`**.

# What was the shot-put scores for the top three competitors in each competition?

Note that we are considering the top three competitors (assumed to mean in each competition, not each event) only.

```{r}
decathlon_analysis$shot_put <- decathlon_data %>% 
  filter(
    rank <= 3,
    event_name == "Shot Put"
  ) %>% 
  select(
    -points,
    -event_name
  ) %>% 
  rename(
    shot_put_score = event_score
  ) %>% 
  arrange(
    competition,
    rank
  )
```

```{r echo = FALSE}
decathlon_analysis$shot_put
```

# What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

```{r}
decathlon_analysis$fast_sprinter <- decathlon_data %>% 
  filter(
    event_name == "Sprint, 400m"
  ) %>% 
  mutate(
    fast_sprinter = ifelse(
      event_score < 50,
      TRUE,
      FALSE
    )
  ) %>% 
  group_by(
    fast_sprinter
  ) %>% 
  summarise(
    mean_points = mean(points)
  ) %>% 
  mutate(
    mean_points = round(mean_points, 2)
  ) %>% 
  arrange(
    desc(mean_points)
  )
```

```{r echo = FALSE}
decathlon_analysis$fast_sprinter
```

The average (competition) points for an decathlete who completes the 400 m sprint in less than 50 seconds is
**`r decathlon_analysis$fast_sprinter$mean_points[1]`**.
The average points for an athlete who completes the 400 m sprint in greater than (or equal to) 50 seconds is
**`r decathlon_analysis$fast_sprinter$mean_points[2]`**.
This is a total difference of
**`r decathlon_analysis$fast_sprinter$mean_points[1]-decathlon_analysis$fast_sprinter$mean_points[2]`**.

Predictably, decathletes who complete the 400 m sprint quickly have greater mean competition-wide points total.
