---
title: "Confidence Intervals Minilab"
date: "2020-04-01"
---

```{r knitr, include = FALSE}
knitr::opts_chunk$set(error = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(infer)
library(janitor)
library(tidyverse)
```

The data set used for this exercise, `ames.csv`, explores the prices and condition of houses sold in in Ames, Iowa over a number of years.

```{r}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()
```

```{r}
glimpse(ames)
```

# Question 1
*Plot a histogram of `sale_price`. Is the distribution normal?*

```{r}
ames %>% 
  ggplot() + 
  aes(
    x = sale_price
  ) + 
  geom_histogram(
    bins = 30,
    col = "white"
  )
```

The data appears to follow a normal distribution, with a right skew.

# Question 2
*Calculate the population parameter mean of `sale_price`. Store it in a variable, as we’ll need this value later when we check if each CI contains the parameter value or not.*

```{r}
ames_sale_mean <- mean(ames$sale_price)
```

# Question 3
Now we are going to:

- Take 1,000 random samples each of size 100 from `sale_price` in `ames`,
- Create a boostrap sampling distribution of `mean(sale_price)` from each 100-observation sample (using 1000 reps),
- Calculate the 95% CI (confidence interval) for each bootstrap distribution,
- Store the upper and lower bounds of the CI in a tibble called `results`,

By using the infer workflow to generate the bootstrap distributions and CIs.

```{r}
# Generate an empty tibble to populate
results <- tibble()

# Start of for loop
for (sample_number in 1:1000) {
  
  # Take a random sample of size 100 from `sale_price`
  sample <- ames %>% 
    select(
      sale_price
    ) %>% 
    rep_sample_n(
      size = 100,
      reps = 1
    ) %>% 
    ungroup()
  
  # Create a bootstrap sampling distribution of `mean(sale_price)` from the above random sample
  bootstrap <- sample %>% 
    specify(
      response = sale_price
    ) %>% 
    generate(
      reps = 1000,
      type = "bootstrap"
    ) %>% 
    calculate(
      stat = "mean"
    )
  
  # Calculate the 95% CI
  ci_95 <- bootstrap %>% 
    get_ci(
      level = 0.95,
      type = "percentile"
    )
  
  # Store result in a vector
  result <- c(
    sample_number = sample_number,
    lower = ci_95[[1]],
    upper = ci_95[[2]]
  )
  
  # Bind result vector to results tibble
  results <- bind_rows(
    results,
    result
  )
  
}


```

# Question 4
*Pipe `results` to `mutate()` to add a new variable `popn_param_in_ci` which will be `TRUE` if the population parameter we calculated earlier is between lower and upper, and `FALSE` otherwise.*

```{r}
results_in_ci <- results %>% 
  mutate(
    popn_param_in_ci = 
      lower <= ames_sale_mean &
      upper >= ames_sale_mean
  )
```
