---
title: "Dog Owners' Survey"
subtitle: "Week 04; Homework"
author: "Miles Drake"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_float: true
---

```{r knitr, include = FALSE}
knitr::opts_chunk$set(error = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries, include = FALSE}
library(tidyverse)
library(here)
```

```{r include = FALSE}
survey_clean <- read_csv(
  here("clean_data/dog_survey_clean.csv")
)
```

The dog owners' survey is a free-hand data set, comprised of British dog owners. This data set collates the self-reported size, sex, and age of their dogs; the amount that they spend on dog food (in GBP); and the respondant's contact information.

# Complete Data Set

```{r}
survey_clean
```

# Analysis

## The Cost of Feeding Larger Dogs

The mean cost of dog food for each self-reported size of dog is tabulated below.

### Code

Dog size is a coded value, where the code is as follows:

| Code | Size |
|------|------|
| 0    | XS   |
| 1    | S    |
| 2    | M    |
| 3    | L    |
| 4    | XL   |


### Results Table

```{r}
survey_clean %>% 
  select(
    dog_size,
    amount_spent_on_dog_food
  ) %>% 
  group_by(
    dog_size
  ) %>% 
  summarise(
    mean_dog_food_cost_gbp = mean(amount_spent_on_dog_food, na.rm = TRUE)
  ) %>% 
  mutate(
    mean_dog_food_cost_gbp = round(mean_dog_food_cost_gbp, 2)
  )
```

We would, intuitively, suppose that larger dogs require a greater investment in dog food. However, a quick glance at the summary data suggests that this is not the case. It would appear that there is no correlation between dog size and cost of dog food.
