---
title: "World Bank Data"
subtitle: "Week 03, Day 1; Homework"
author: "Miles Drake"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_float: true
---

```{r knitr, include = FALSE}
knitr::opts_chunk$set(error = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(janitor)
library(tidyverse)
library(outliers)
```

# MVP

##

```{r}
women <- read_csv("data/women_in_gov.csv", skip = 4)
```

##

```{r}
women <- rename(
  women,
  "country_name" = "Country Name",
  "country_code" = "Country Code",
  "indicator_name" = "Indicator Name",
  "indicator_code" = "Indicator Code"
)
```

##

```{r}
unique(women$indicator_name)
unique(women$indicator_code)
unique(women$X64)
```

```{r}
women <- select(
  women,
  -indicator_name,
  -indicator_code,
  -X64
)
```

##

```{r}
women <- pivot_longer(
  women,
  cols = "1960":"2018",
  names_to = "year",
  values_to = "percent"
)
```

##

```{r}
women_na <- women %>% 
  filter(
    is.na(percent)
  )
```

```{r}
unique(women_na$percent)
sum(
  is.na(women_na$percent)
)
```

```{r}
women <- women %>% 
  filter(
    !is.na(percent)
  )
```


```{r}
women
```

##

```{r}
ggplot(women) +
  aes(y = percent) +
  geom_boxplot()
```

```{r}
women <- women %>%
  mutate(
    zscore = scores(percent),
    is_outlier = zscore < -3 | zscore > 3,
    zscore = round(zscore, 2)
  )
```

```{r}
filter(
  women,
  is_outlier
)
```

##

Rwanda and Bolivia are famous for having lower houses of parliament where more than 50 per cent of the chamber are female deputies. These outliers are *valid* data, but they make visual analysis of the rest of the world more difficult. It is, arguably, worth removing Rwanda and Bolivia from the data set to focus on the rest of the world.

```{r}
women_row <- women %>%
  filter(
    !(country_code %in% c("BOL", "RWA"))
  )
```

##

```{r}
women_row_mean <- women_row %>% 
  group_by(country_name) %>% 
  summarise(
    mean_percent = mean(percent)
  ) %>% 
  arrange(
    desc(mean_percent)
  )
```

```{r}
head(women_row_mean, 10)
tail(women_row_mean, 10)
```

##

Which countries have had the greatest change in proportion of women deputies for between their earliest and latest recorded dates?

```{r}
women_row_change <- women_row %>% 
  arrange(
    country_name,
    year
  ) %>% 
  group_by(country_name) %>% 
  mutate(
    diff = percent - lag(percent)
  ) %>% 
  summarise(
    cum_diff = sum(diff, na.rm = TRUE)
  ) %>% 
  mutate(
    cum_diff = round(cum_diff, 2)
  ) %>% 
  arrange(
    desc(cum_diff)
  )
```

```{r}
head(women_row_change, 10)
tail(women_row_change, 10)
```
